\documentclass{llncs}

%\usepackage{graphicx}
%
\usepackage[named]{algo}

\begin{document}


\title{Image Segmentation by Size-Dependent Single Linkage
  Clustering of a Watershed Basin Graph}

\subtitle{Supplementary Material}

\author{{*}{*}{*}{*}{*}{*}{*}{*}{*}{*}{*}{*}{*}{*}{*}{*}{*}{*}{*}}


\institute{{*}{*}{*}{*}{*}{*}{*}{*}{*}{*}{*}\\
\texttt{{*}{*}{*}{*}{*}{*}{*}{*}{*}}\\
{*}{*}{*}{*}{*}{*}{*}{*}{*}{*}{*}\\
\texttt{{*}{*}{*}{*}{*}{*}{*}{*}{*}}}

\maketitle


\section{The Watershed Transform Algorithm}\label{sec:Introduction}

\begin{algorithm}{CreateSDG}[$G$]{
    \label{algo:createsdg}
    \qinput{A weighted graph $G$}
    \qoutput{Steepest descent graph $G'$}
    \qcomment{Creates the steepest descent graph}
    \qcomment{Assumes ordered vertices $v_1,\dots,v_n$}
  }
  Create $G'=(V,E'=\emptyset)$ \\
  $n \qlet |V|$ \\
  \qfor $i \qlet 1$ \qto $n$ \\
  \qdo $D(v_i) \qlet \infty$ \qrof \\
  \qfor $e = \{v_i,v_j\} \in E$ in any order\\
  \qdo $D(v_i) \qlet \min\{D(v_i),w(e)\}$ \\
  $D(v_j) \qlet \min\{D(v_j),w(e)\}$ \qrof \\
  \qfor $e = \{v_i,v_j\} \in E$ in any order \\
  \qdo \qqif $D(v_i) = w(e)$ \qqthen insert $(v_i,v_j)$ to $E'$ \\
  \qqif $D(v_j) = w(e)$ \qqthen insert $(v_j,v_i)$ to $E'$ \qrof \\
  \qreturn $G'$
\end{algorithm}


\begin{algorithm}{ModifySDG}[$G'=(V,E')$]{
    \label{algo:modifysdg}
    \qinput{Steepest descent graph}
    \qoutput{Modified steepest descent graph}
    \qcomment{Assumes ordered vertices $v_1,\dots,v_n$}
  }
  Initialize a queue $Q$ \\
  $n \qlet |V|$ \\
  \qfor $i \qlet 1$ \qto $n$ \\
  \qdo $o \qlet \qfalse$ \\
  $b \qlet \qfalse$ \\
  \qfor all edges $(v_i,u) \in E'$ \\
  \qdo \qif $(u,v_i) \in E'$ \\
  \qthen $o \qlet \qtrue$ \\
  \qelse $b \qlet \qtrue$ \qfi \qrof \\
  \qif $o$ \qand $b$ \\
  \qthen mark $v_i$ as visited \\
  add $v_i$ to the end of the queue $Q$ \qfi \qrof \\
  \qwhile $Q \neq \emptyset$ \\
  \qdo let $u$ be the first element of $Q$ and remove it from $Q$\\
  \qfor all edges $(u,v) \in E'$ such that $(v,u)$ exists in $E'$\\
  \qdo remove $(u,v)$ from $E'$ \\
  \qif $v$ is visited \\
  \qthen remove $(v,u)$ from $E'$ \\
  \qelse mark $v$ as visited, add $v$ to the end of $Q$ \qfi \qend \qrof \\
  \qreturn $G'=(V,E')$
\end{algorithm}


\begin{algorithm}{GetWatershedBasins}[$G'=(V,E')$]{
    \label{algo:modifysdg}
    \qinput{Steepest descent graph}
    \qoutput{Watershed basins, function $B$ such that $B(v)$ }
    \qcomment{Assumes ordered vertices $v_1,\dots,v_n$}
  }
  $next \qlet 0$ \\
  $n \qlet |V|$ \\
  mark all vertices as not visited \\
  \qfor $i \qlet 1$ \qto $n$ \\
  \qdo
\end{algorithm}



Watershed Transform

2) prove $T_{\min}$ claim.
-

\section{Hierarchical Clustering of the Watershed Basin Graph}\label{sec:Others}

The following algorithm and theorem were introduced in the main manuscript.

\textbf{Algorithm 1 } Size-dependent single linkage clustering
\begin{enumerate}
\item Order $E_{W}$ into $\pi(e_{1},\dots,e_{n})$, by non-decreasing edge
weight.
\item Start with basins as singleton clusters $S^{0}=\{C_{1}=\{B_{1}\},C_{2}=\{B_{2}\},\dots\}$
\item Repeat step $4$ for $k=1,\dots,n$
\item Construct $S^{k}$ from $S^{k-1}$. Let $e_{k}=\{B_{i},B_{j}\}$ be
the $k$-th edge in the ordering. Let $C_{i}^{k-1}$ and $C_{j}^{k-1}$
be components of $S^{k-1}$ containing $B_{i}$ and $B_{j}$. If $C_{i}^{k-1}\neq C_{j}^{k-1}$
and $\Lambda(C_{i}^{k-1},C_{j}^{k-1})$ is not satisfied then $S^{k}$ is created from
$S^{k-1}$ by merging $C_{i}^{k-1}$ and $C_{j}^{k-1}$, otherwise
$S^{k}=S^{k-1}.$
\item Return the hierarchical segmentation $(S^{0},\dots,S^{n})$
\end{enumerate}
\textbf{Theorem 1 }\emph{The highest level of the hierarchical segmentation
produced by algorithm (1) will have the predicate $\Lambda$ satisfied
for all pairs of the clusters. The complexity of the algorithm is
$\left|E_{W}\right|\log\left|E_{W}\right|$. The algorithm can be
modified to consider only the edges of the minimum cost spanning tree
of $G_{W}$.}

1. by contradiction. Assume lambda not satisfied for some edge $e_W$ and connecting some clusters A and B in the final segmentation.. that means...
at the time when blah was considered they could have been only smaller.. bla...

2. The sorting is dominnant, the second part is using union find blah blah

3. Assume edge $e_w$ not on the MST is considered and has unsatisfied predicate. let $e_w$ connect two basins A and B in the watershed basin graph.
as $e_w$ is not on the MST, there exist a path between A and B such that all the edges have smaller or values than $e_w$, so they have all been considered
befire $e_w$. WLG let S(A) < S(B). then $e_w \le \tau(S(A))$. look at the path $e_1$, $e_2$... $e_n$ on the mst from A to B.
\section{More Results}\label{sec:Conclusion}

More results


\end{document}
